\begin{abstractslong}

\addcontentsline{toc}{chapter}{Abstract}

Of recent times, there has been an increasing awareness about free and open source softwares in the tech-savvy community and the added advantages that they bring in to them but the trend is yet to catch up among non-technical masses. There are two main reasons behind this lag : 
\begin{itemize}
\item Most of them aren't aware. They are oblivious to the existence of FOSS or are not educated on the importance of it.
\item FOSSs hit the bull’s eye over the security aspect but it lags in one another crucial dimension, one which encompasses errors and glitches (not to say that they aren't present in other proprietary software but they are well hidden for obvious reasons) that are so ubiquitous in these softwares that it becomes imperative to get rid of them as soon as possible.
\end{itemize}


Our aim throughout the project is to develop a platform that shall serve as a catalog for free and open source software that form best alternatives to the in-market proprietary softwares. This serves the greater good that free and/or open source licenses have to offer and at the same time, bring about a change that is positive and most welcome.

Furthermore, the platform shall help bring the bugs discussed above into open scrutiny by creating a unified platform for people who observe these glitches to report it and people who are willing to solve some issues can look up from here and propose their solutions. This effectively bridges the gap between the general public who are preparing to be at the behest of these softwares and the developers who can solve them.
\\

We three having personally used these softwares and attended scores of seminars on them have been driven and inclined towards the ideology that free and open source softwares hold up. We believe in freedom of code and software. We believe that it is of paramount importance to be able to look into the inner workings of our computers and its nuances.

Furthermore, this particular project was chosen because of the amount of learning it offers and what’s best, it caters to our individual passions just right. The bulk of things that we shall be learning in this project are more than relevant to the present times and most importantly, shall train us to be better software engineers. We have seen through the possibilities in this arena and we just can’t wait to get started.
\end{abstractslong}