\begin{acknowledgementslong}

\addcontentsline{toc}{chapter}{Acknowledgments}

Any success is never a lone task of an individual or a single group. There are always numerous contributions from all the great souls surrounding us to our endeavors.

We would like to start by remembering and thanking our founder president and His Holiness \textbf{Dr. Sree Sree Shivakumara Swamiji} to have founded this great legacy of Siddaganga Institute of Technology and creating a holy abode of wisdom for all us to reap from. We further extend our thanks to our president \textbf{Sree Sree Siddalinga Swamiji} for being an active help and guide to our institute.

We thank our Director, \textbf{Dr. M. N. Channabasappa} for providing us with excellent infrastructure and ever lasting support.

We thank our CEO, \textbf{Dr. Shivakumaraiah} for constant inspiration and persistent motivation.

We thank our Principal, \textbf{Dr. K P Shivananda} for his generosity and genial demeanor.

We thank our Head Of Department, \textbf{Dr. R Sumathi} for being an inspiration and highly supportive in all our endeavors as students.

We are highly indebted to \textbf{Mr. C P Prabodh} for his much-needed guidance and constant supervision as well as for providing necessary information regarding the project. We are ever so thankful to him for introducing us to the Free Software Movement.

We thank our Mini Project Convener, \textbf{Mr. A V Krishna Mohan} for providing consistent information and guidance regarding the whole procedure. 


We thank \textbf{Free Software Movement Karnataka} members to extend our guidance in the initial stages of our project and introducing us to nuances of the movement. It has helped us a lot.

And lastly, we thank every single one of you who have contributed to this project in the form of advice, suggestions or improvements.

Thank you all.

\end{acknowledgementslong}

