\chapter{Conclusion And Future Scope}

\section{Conclusion}

Free and open source softwares are important choices towards safeguarding ourselves as well as an appropriate preference for developers and users alike. Our project tries to do what little we can to make this digital world a better place. Applications like this reinforce the need and importance of FOSS as well as open an opportunity to experience life differently. 

We started out as novices in web-development with an aim to contribute but we are now a few steps ahead in our journey toward web-development. This is a huge bring back from the project for us. Furthermore, we had made some real hard decisions which weren't easy to come by. We had a look at various parameters and make sense out of the unknown. This learning experience shall stay with us forever.

After having looked at the development across back-end, front-end and middleware stages, it was a very holistic experience. Learning so much in so little time was very fulfilling and having done something towards our beloved community was really amazing.

We really enjoyed doing this project and more importantly, learned so much along the journey that we are indebted to it. This project shall also find a place in the muse of FOSS evangelists and shall be taken forward as it finds its place in this dynamic world. We hope to see AlterFOSS grow further as well as bring about a moral conscience in all those who choose to use it and bring about a change in their lives. The next section shall talk about the future scope of this project and how we can improve on the shortcomings of the present.

\section{Future Scope}
There were many things that we set out to do and there are many things among them that we did. But as always is the case, we still feel that there is a scope for improvement and we shall point out just that in this section.

First things first, so far we have restricted ourselves to suggest alternatives based on the software but it doesn't have to end there. We can suggest softwares based on the functionality they provide and based on the requirements specified. We can add comment sections and also an automated feedback section that would require a touch of intelligence to the whole system.

As we come to the end of our report, we would want to end it by noting that there is far too much that can be done and we are open to suggestions and advice. As this project is very close to our ideals, we shall continue to provide support to it and bring about all that we discussed so far in a more optimized way and also, let the community make contributions too.